Compiling refinement types to dependent types

### 2020-07-11 tex/paper.tex
Actually add the commands for core units
Start working on the terms translation
Use \tran* things in the theorems as well

\newcommand{\unit}{u}
\newcommand{\Unit}{\textbf{Unit}}
\newcommand{\Int}{\textbf{Int}}

@@

@@

\begin{theorem}[Well-typedness preservation]
  For any well-typed surface language term $\nonterm{es}$,
  the result of the translation $\mu_\epsilon(\nonterm{es})$ is ``equivalently'' typeable in the core language:
  \[
    \nonterm G \vdash \nonterm{es} : \nonterm{ts} \implies \mu_\Gamma(\nonterm G) \vdash \mu_\epsilon(\nonterm{es}) : \mu_\tau(\nonterm{ts})
  \]
\end{theorem}
\begin{proof}
\end{proof}

\begin{theorem}[Evaluation equivalence]
  If a well-typed surface language term $\nonterm{es}$ evaluates to v, then $\mu_\varepsilon(\nonterm{es})$ evaluates to $\mu_\varepsilon(v)$:
  %TODO symbols and all that for v
\end{theorem}
\begin{proof}
\end{proof}

>>>>

\newcommand{\unit}{u}
\newcommand{\Unit}{\textbf{Unit}}
\newcommand{\unitc}{\hat{u}}
\newcommand{\Unitc}{\widehat{\textbf{Unit}}}
\newcommand{\Int}{\textbf{Int}}

@@

\paragraph{Terms.}
Finally we define $\tranterm$:
\begin{equation}
\begin{aligned}
  & \tranterm(x) &&
    \triangleq x                                                              \\
  & \tranterm(\lambda x : \nonterm{ts}. \nonterm{es})  &&
    \triangleq \lambda x : \tranty(\nonterm{ts}). \tranterm(\nonterm{es})     \\
  & \tranterm(\nonterm{es}_1 \nonterm{es}_2)  &&
    \triangleq \tranterm(\nonterm{es}_1) \tranterm(\nonterm{es}_2)            \\
\end{aligned}
\end{equation}

@@

\begin{theorem}[Well-typedness preservation]
  For any well-typed surface language term $\nonterm{es}$,
  the result of the translation $\tranterm(\nonterm{es})$ is ``equivalently'' typeable in the core language:
  \[
    \nonterm G \vdash \nonterm{es} : \nonterm{ts} \implies \tranctx(\nonterm G) \vdash \tranterm(\nonterm{es}) : \tranty(\nonterm{ts})
  \]
\end{theorem}
\begin{proof}
\end{proof}

\begin{theorem}[Evaluation equivalence]
  If a well-typed surface language term $\nonterm{es}$ evaluates to v, then $\tranterm(\nonterm{es})$ evaluates to $\tranterm(v)$:
  %TODO symbols and all that for v
\end{theorem}
\begin{proof}
\end{proof}
